---
title: "CTL_Assignment"
author: "Fan Feng"
date: "2021/3/5"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1 
A machine produces rope at a mean rate of mean of 4 feet per minute with standard
deviation of 5 inches. Assume that the amounts produced in different minutes are independent and
identically distributed, approximate the probability that the machine will produce at least 250 feet
in one hour.
```{r}

```


#Problem 2 
Assume that the distribution of the number of defects on any given bolt of cloth
is the Poisson distribution with mean 5, and the number of defects on each bolt is counted for a
random sample of 125 bolts. Determine the probability that the average number of defects per bolt
in the sample will be less than 5.5 defects per bolt.
```{r}

```


#Problem 3 
Suppose that the proportion of defective items in a large manufactured lot is 0.1.
What is the smallest random sample of items that must be taken from the lot in order for the
probability to be at least 0.99 that the proportion of defective items in the sample will be less than
0.13?
```{r}

```

#Problem 4 
Suppose that 16 digits are chosen at random with replacement from the set 0, . . . , 9.
What is the probability that their average will lie between 4 and 6?
```{r}

```

#Problem 5 
Select a skewed distribution from which to sample. Using R, demonstrate the
convergence of the mean value of your samples to the Normal distribution. Assume you are making
this demonstration to someone who has little or no statistical training. Your demonstration should
take no more than 10 minutes. Along with your code, outline the commentary you would use in
your demonstration.
```{r}

```

