---
title: "Empirical Distribution, Kolmogorov-Smirnov Test"
author: "Fan Feng"
date: "2021/3/12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("tidyverse","magrittr")
```

## Fiji earthquakes

Data on the magnitudes of earthquakes near Fiji are on Blackboard under the Class-21
tab. Estimate the cdf F(x). Compute and plot a 95% confidence envelope for F. Find an
approximate 95 percent confidence interval for F(4.9) − F(4.3).
```{r}
options(digits=6, scipen=999)
fiji_data<-read.csv("fijiquakes.csv",sep = "")
fiji_cdf<-ecdf(fiji_data$mag)
nfiji<-nrow(fiji_data)
alpha=.05
X<-seq(0,max(fiji_data$mag),length=1000)
fx<-fiji_cdf(X)
epsilon<-sqrt((1/(2*nfiji))*log(2/alpha))
L<-pmax(fx-epsilon,0)
U<-pmin(fx+epsilon,1)
plot.ecdf(fiji_cdf,pch=20)
lines(X,L,type="l",lty=1,col="red")
lines(X,U,type="l",lty=1,col="red")
```

```{r}

E<-fiji_cdf(4.9)-fiji_cdf(4.3)
varfiji<-function(x){
  vf<-(fijicdf(x)*(1-fijicdf(x)))/nfiji
  return(vf)
}
v<-varfiji(4.9)+varfiji(4.3)
sd<-sqrt(v)
cl<-round(E-2*sd,2)
cr<-round(E+2*sd,2)
paste("Confidence interval at .05 is [",cl,",",cr,"]")
```

## Old faithful
Data on eruption times and waiting times between eruptions of the old faithful geyser
(located in Yellowstone National Park) are posted on Blackboard under the Class-21 tab.
Estimate the mean waiting time and compute a standard error for the estimate. Also,
calculate a 90 percent confidence interval for the mean waiting time. Finally, estimate the
median waiting time. We will use this calculation of the median in our discussions next
week.
```{r}
geysers <- read_csv("geysers.csv")
cdf_geysers<- ecdf(geysers$waiting)
plot.ecdf(cdf_geysers)
n <- length(geysers$waiting)
n
alpha =  .05
x <- seq(0, max(geysers$waiting), length=n)
fx <- cdf_geysers(x)

epsilon <- sqrt((1/(2*n))*log(2/alpha))

L <- pmax(fx - epsilon, 0)
U <- pmin(fx + epsilon, 1)

plot.ecdf(cdf_geysers, pch=20)
lines(x, L, type="l", lty=1, col="red" )
lines(x, U, type="l", lty=1, col="red" )

mean(geysers$waiting) # 71 mins

se <- sd(geysers$waiting)/sqrt(length(geysers$waiting))

# 90% confidence interval: 69.65 to 72.25
mean(geysers$waiting) + 1.645*se
mean(geysers$waiting) - 1.645*se

median(geysers$waiting) # 76 mins
```

## KS problem
Use the Kolmogorov-Smirnov test to test the hypothesis that the 25 values in the table below form a random sample from the uniform distribution on the interval [0, 1].

```{r}
set.seed(1)
x_sim<-rep(0,10000)
y_sim<-rep(0,10000)
for(i in 1:5000)
{
  x_sim[i]=runif(1,0,1/2)
  y_sim[i]=runif(1,0,3/4)
  while(y_sim[i]>3/2*x_sim[i]){
    x_sim[i]=runif(1,0,1/2)
    y_sim[i]=runif(1,0,3/4)
  }
}
for(i in 5000:10000)
{
  x_sim[i]=runif(1,1/2,1)
  y_sim[i]=runif(1,3/4,1)
  while(y_sim[i]>1/2*(x_sim[i]+1)){
    x_sim[i]=runif(1,1/2,1)
    y_sim[i]=runif(1,3/4,1)
  }
}
plot(x_sim,y_sim)
```
0.42 0.06 0.88 0.40 0.90
0.38 0.78 0.71 0.57 0.66
0.48 0.35 0.16 0.22 0.08
0.11 0.29 0.79 0.75 0.82
0.30 0.23 0.01 0.41 0.09
Using the table above, test the hypothesis that the 25 values are a random sample from a
continuous distribution with pdf:
```{r}
ks_1<-c(0.42,0.06,0.88,0.40,0.90,0.38,0.78,0.71,0.57,0.66,0.48,0.35,0.16,0.22,0.08,0.11,0.29,0.79,0.75,0.82,0.30,0.23,0.01,0.41,0.09)
ks.test(ks_1,x_sim)
```


```{r,eval=FALSE,include=FALSE}
cdf_real<-function(x){
  if(x>0&&x<1){
  y<-ifelse(x > 1/2, 1/2 * (x+1), 3/2 * x)
  }else {y=0}
  return(y)
}
ks.test(ks_1,"cdf_real")
```

